\section{Discussion}
This section takes this chapter and boils it down to a list of topics that describe the security issues found.
This list is meant as a summary and tries to combine the attack trees in order to show which topics are exposed.




\subsection{Privacy issues}
When an attacker is able to obtain the consumers power consumption they are able to obtain private information, see \cref{smart_meter_privacy}.
An attacker has the following options to obtain the power consumption:
\begin{itemize}
\item Get remote access to the smart meter(see ``Compromise SM'' \cref{})
\item Get access to a validated client(see ``Compromise client'' \cref{})
\item Have access to the consumers power cables(see ``Monitor consumption with ECM'' \cref{})
\end{itemize}

To completely solve the privacy issues the listed items above have to be solved.
To obtain prioritised list one could add costs to the attack trees with the listed sub trees above.


\subsection{Price manipulation}
When an attacker is able to obtain access to the prices being send from the Electrical Company to the SM the attacker has the option to modify these prices.
This can be done on a big scale or just against individual consumers.
To obtain access to connections sending the  price information an attacker has the following options:
\begin{itemize}
\item Get remote access to the smart meter(see ``Compromise SM'' \cref{})
\item Get access to a validated client(see ``Compromise client'' \cref{})
\end{itemize}

To completely solve the privacy issues the listed items above have to be solved.
To obtain prioritised list one could add costs to the attack trees with the listed sub trees above.

\subsection{Consumption data manipulation}
\bruno{Same as above?}

\subsection{Obtaining access to home network}
In the following we assume that the SM is connected to the consumers home automation network or just home network.
An attacker has the possibility to infiltrate the consumers home network.



\subsection{Control home appliances}
The attacker can


\subsection{Switch off the SM}
If the attacker can get access to the SM in a way so that he can control it he has the possibility to switch the electricity by the consumer off, see \cref{off_switch}.

This could be a major distributed attack.
