%!TEX root=../master.tex

\section{Concerns regarding the remote access-ability of smart meters}\label{off_switch}
As the smart grid and smart meters are getting more common an important observation was made by \citet{offswitch}.
This observation is regarding the possibility of the electrical company to switch off the smart meter.
The purpose of a remote off-switch could be to switch of the electricity if a customer is not paying.
When having smart meters controlled one place this place could be a target by terrorists, other countries or by a group of activists. \stefan{er det nogle aktører vi skal overveje at have med i resten af analysen?}
\mikael{I think we could have one of these attackers with a `turn-off-power'-attack-tree (if we used them all they would probably be too similar).}
By switching off smart meters in a whole region, the region would become paralysed because of the necessity of electricity.
It would also be possible to do energy theft against electrical companies.

\paragraph{Large scale consequences}
In a scenario where millions of smart meters are deployed and controlled from a central control unit without taking possible attacks against the off-switch into account could be very dangerous.
\citet{offswitch} states that this is happening in the United Kingdom.
This means that there probably are a lot of vulnerabilities in the setup.
If an attacker gets access to the central control unit he has the ability to compromise all the connected smart meters.
By also tampering the cryptography of the smart meters the attack could last for weeks for some consumers.
People would die from basic diseases as for instance hypothermia because of lack of electricity at hospitals.
The region it would effect would be in chaos.

\paragraph{Attackers}
Possible attackers for such an attack could be:
\begin{itemize}
\item Countries when there is international tension.
\item A terrorist organisation.
\item Environmental activists which are frustrated with governments not taken the environment seriously.
\item A criminal who switches off all or some smart meters from an electrical company and demands money for switching them on again.
\end{itemize}
\stefan{samme liste blev nævnt i starten, skal det eventuelt slettes det ene sted?}
\mikael{I think the list is good, as long as it doesn't mention the exact same as above. The other mention could probably be shortened or generalized.}

\bruno{Skal vi have deres bud på en løsning med?}
\mikael{I think so, as long as we keep it short.}
